Experimental Results \\ \mbox{ } \\ of a Safety Checker for Petri nets

### 2014-01-31 doc/benchmark-tables.tex
Updated benchmark tables with new method inv-ref-min

\usepackage{amsmath}
\usepackage[usenames,dvipsnames]{color}
\usepackage{multirow}
\usepackage{listings}
\usepackage[a4paper, landscape, top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}

@@

\begin{description}
  \item[P] Number of places in the petri net.
  \item[T] Number of transitions in the petri net.
  \item[R] Result of our tool. It is + if our tool can prove safety or find an invariant and - otherwise.
  \item[I] Number of iterations. This is the number of traps used for refinement or the number of times an invariant is minimized.
  \item[T] Running time of our tool in seconds.
\end{description}

@@

\begin{description}
  \item[Safety] Method Safety over reals.
  \item[Safety-Int] Method Safety over integers.
  \item[Refinement] Method Safety by Refinement over reals.
  \item[Refinement-Int] Method Safety by Refinement over integers.
  \item[Invariant] Method Invariant.
  \item[Inv-Min] Method Invariant Minimization.
  \item[Inv-Ref] Method Invariant by Refinement.
\end{description}

@@

The set of benchmarks consists of 77 benchmarks, 26 positive and 51 negative.
Table~\ref{bfc-experiments}, \ref{bfc-experiments-2} and \ref{bfc-experiments-3}
show the experimental results.

@@

  \begin{tabular}{ | l | r | r | *{17}{ r | } } %

@@

         & \multicolumn{2}{|c|}{Safety-Int}

@@

         & \multicolumn{3}{|c|}{Refinement-Int}

@@

         & \multicolumn{2}{|c|}{Inv-Ref} \\

@@

@@

        & R & T \\

@@

        \multicolumn{20}{|c|}{Positive Benchmarks} \\

@@

cprover-PN/abp & 42 & 43 & + & 0.19 & + & 0.18 & + & 0 & 0.13 & + & 0 & 0.17 & + & 0.26 & + & 2 & 0.56 & + & 0.42 \\
cprover-PN/basicME & 18 & 17 & + & 0.13 & + & 0.15 & + & 0 & 0.13 & + & 0 & 0.17 & + & 0.25 & + & 0 & 0.30 & + & 0.39 \\
cprover-PN/bingham\_h150 & 309 & 457 & + & 0.35 & + & 0.35 & + & 0 & 0.40 & + & 0 & 0.35 & + & 0.57 & + & 0 & 0.81 & + & 0.93 \\
cprover-PN/bingham\_h25 & 59 & 82 & + & 0.17 & + & 0.19 & + & 0 & 0.17 & + & 0 & 0.18 & + & 0.30 & + & 0 & 0.36 & + & 0.45 \\
cprover-PN/bingham\_h250 & 509 & 757 & + & 0.61 & + & 0.55 & + & 0 & 0.55 & + & 0 & 0.57 & + & 0.85 & + & 0 & 1.22 & + & 1.43 \\
cprover-PN/bingham\_h50 & 109 & 157 & + & 0.22 & + & 0.22 & + & 0 & 0.19 & + & 0 & 0.19 & + & 0.34 & + & 0 & 0.46 & + & 0.55 \\
cprover-PN/bingham\_h500 & 1009 & 1507 & + & 1.20 & + & 1.09 & + & 0 & 1.20 & + & 0 & 1.11 & + & 1.74 & + & 0 & 2.89 & + & 3.00 \\
cprover-PN/clientserver & 13 & 11 & + & 0.13 & + & 0.12 & + & 0 & 0.15 & + & 0 & 0.14 & + & 0.27 & + & 0 & 0.32 & + & 0.38 \\
cprover-PN/csm & 28 & 27 & + & 0.14 & + & 0.15 & + & 0 & 0.13 & + & 0 & 0.13 & + & 0.26 & + & 0 & 0.32 & + & 0.35 \\
cprover-PN/gsm & 73 & 156 & + & 0.26 & + & 0.29 & + & 0 & 0.21 & + & 0 & 0.20 & + & 0.64 & + & 0 & 0.68 & + & 0.78 \\
cprover-PN/handover & 126 & 255 & + & 0.23 & + & 0.23 & + & 0 & 0.25 & + & 0 & 0.26 & + & 0.37 & + & 0 & 0.50 & + & 0.60 \\
cprover-PN/keycard & 59 & 78 & + & 0.16 & + & 0.15 & + & 0 & 0.21 & + & 0 & 0.15 & + & 0.33 & + & 0 & 0.36 & + & 0.49 \\
cprover-PN/lamport & 30 & 27 & - & 0.19 & - & 0.18 & - & 0 & 0.20 & - & 0 & 0.21 & - & 0.14 & - & 0 & 0.17 & - & 0.23 \\
cprover-PN/mesh2x2 & 66 & 69 & + & 0.20 & + & 0.20 & + & 0 & 0.15 & + & 0 & 0.20 & + & 0.27 & + & 0 & 0.37 & + & 0.43 \\
cprover-PN/multipoll & 35 & 41 & + & 0.15 & + & 0.15 & + & 0 & 0.16 & + & 0 & 0.14 & + & 0.26 & + & 0 & 0.32 & + & 0.43 \\
cprover-PN/newdekker & 51 & 48 & - & 0.18 & - & 0.18 & - & 0 & 0.22 & - & 0 & 0.25 & - & 0.15 & - & 0 & 0.15 & - & 0.24 \\
cprover-PN/newrtp & 12 & 14 & + & 0.15 & + & 0.12 & + & 0 & 0.15 & + & 0 & 0.14 & + & 0.27 & + & 0 & 0.30 & + & 0.40 \\
cprover-PN/peterson & 39 & 36 & - & 0.15 & - & 0.16 & - & 0 & 0.27 & - & 0 & 0.21 & - & 0.15 & - & 0 & 0.14 & - & 0.22 \\
cprover-PN/phones & 51 & 87 & + & 0.16 & + & 0.18 & + & 0 & 0.16 & + & 0 & 0.16 & + & 0.30 & + & 0 & 0.37 & + & 0.43 \\
cprover-PN/reaction & 19 & 15 & + & 0.14 & + & 0.14 & + & 0 & 0.14 & + & 0 & 0.14 & + & 0.24 & + & 0 & 0.34 & + & 0.37 \\
cprover-PN/reaction3 & 22 & 18 & + & 0.16 & + & 0.13 & + & 0 & 0.13 & + & 0 & 0.15 & + & 0.25 & + & 0 & 0.32 & + & 0.37 \\
cprover-PN/reaction4 & 16 & 13 & + & 0.14 & + & 0.15 & + & 0 & 0.14 & + & 0 & 0.13 & + & 0.28 & + & 0 & 0.33 & + & 0.36 \\
cprover-PN/read-write & 36 & 31 & + & 0.16 & + & 0.20 & + & 0 & 0.14 & + & 0 & 0.14 & + & 0.28 & + & 0 & 0.34 & + & 0.43 \\
cprover-PN/restriction & 15 & 10 & + & 0.14 & + & 0.14 & + & 0 & 0.13 & + & 0 & 0.14 & + & 0.24 & + & 0 & 0.32 & + & 0.40 \\
cprover\_software\_analysis/conditionals\_vs\_satabs.2 & 214 & 281 & + & 0.27 & + & 0.25 & + & 0 & 0.27 & + & 0 & 0.25 & + & 0.44 & + & 0 & 0.55 & + & 0.65 \\
cprover\_software\_analysis/rand\_cas\_vs\_satabs.2 & 110 & 139 & + & 0.19 & + & 0.21 & + & 0 & 0.20 & + & 0 & 0.23 & + & 0.36 & + & 0 & 0.47 & + & 0.50 \\

@@

        \multicolumn{20}{|c|}{Negative Benchmarks} \\

@@

cprover-PN/kanban & 26 & 29 & - & 0.18 & - & 0.17 & - & 0 & 0.23 & - & 0 & 0.20 & - & 0.14 & - & 0 & 0.14 & - & 0.21 \\
cprover-PN/leabasicapproach & 30 & 27 & - & 0.16 & - & 0.16 & - & 0 & 0.24 & - & 0 & 0.23 & - & 0.16 & - & 0 & 0.15 & - & 0.22 \\
cprover-PN/platoon & 20 & 17 & - & 0.17 & - & 0.14 & - & 0 & 0.21 & - & 0 & 0.23 & - & 0.14 & - & 0 & 0.16 & - & 0.24 \\
cprover-PN/platoonFiniteHandlerPoly & 19 & 16 & - & 0.15 & - & 0.16 & - & 0 & 0.24 & - & 0 & 0.22 & - & 0.13 & - & 0 & 0.13 & - & 0.20 \\
cprover-PN/pncsacover & 64 & 68 & - & 0.19 & - & 0.18 & - & 0 & 0.28 & - & 0 & 0.25 & - & 0.16 & - & 0 & 0.17 & - & 0.28 \\
cprover-PN/reaction2 & 13 & 11 & - & 0.15 & - & 0.14 & - & 0 & 0.21 & - & 0 & 0.19 & - & 0.14 & - & 0 & 0.12 & - & 0.25 \\
cprover-PN/reaction5 & 11 & 8 & - & 0.14 & - & 0.14 & - & 1 & 0.39 & - & 1 & 0.44 & - & 0.12 & - & 0 & 0.14 & - & 0.42 \\

@@

        \multicolumn{20}{|c|}{Negative Benchmarks (continued)} \\

@@

cprover\_software\_analysis/Boop\_simple\_vf\_satabs.1 & 31 & 31 & - & 0.16 & - & 0.15 & - & 0 & 0.23 & - & 0 & 0.22 & - & 0.14 & - & 0 & 0.14 & - & 0.21 \\
cprover\_software\_analysis/Boop\_simple\_vf\_satabs.2 & 330 & 7489 & - & 3.39 & - & 3.27 & - & 0 & 5.59 & - & 0 & 5.62 & - & 2.93 & - & 0 & 3.05 & - & 5.36 \\
cprover\_software\_analysis/Function\_Pointer3\_vs\_satabs.1 & 40 & 71 & - & 0.17 & - & 0.16 & - & 1 & 0.52 & - & 1 & 0.49 & - & 0.15 & - & 0 & 0.17 & - & 0.49 \\
cprover\_software\_analysis/Function\_Pointer3\_vs\_satabs.2 & 306 & 841 & - & 0.53 & - & 0.56 & - & 0 & 0.82 & - & 1 & 1.55 & - & 0.45 & - & 0 & 0.49 & - & 0.85 \\
cprover\_software\_analysis/Function\_Pointer3\_vs\_satabs.3 & 2826 & 8961 & - & 8.12 & - & 8.86 & - & 0 & 10.21 & - & 0 & 11.29 & - & 7.49 & - & 0 & 7.56 & - & 10.19 \\
cprover\_software\_analysis/buggy\_spaghetti\_vf\_satabs.1 & 78 & 115 & - & 0.18 & - & 0.18 & - & 0 & 0.31 & - & 0 & 0.27 & - & 0.20 & - & 0 & 0.17 & - & 0.29 \\
cprover\_software\_analysis/buggy\_spaghetti\_vf\_satabs.2 & 326 & 697 & - & 0.50 & - & 0.47 & - & 0 & 0.77 & - & 0 & 0.77 & - & 0.43 & - & 0 & 0.47 & - & 0.72 \\
cprover\_software\_analysis/conditionals\_vs\_satabs.1 & 50 & 55 & - & 0.18 & - & 0.17 & - & 0 & 0.24 & - & 0 & 0.25 & - & 0.15 & - & 0 & 0.15 & - & 0.25 \\
cprover\_software\_analysis/constants\_vf\_satabs.1 & 26 & 25 & - & 0.15 & - & 0.15 & - & 0 & 0.25 & - & 0 & 0.22 & - & 0.15 & - & 0 & 0.13 & - & 0.22 \\
cprover\_software\_analysis/constants\_vf\_satabs.2 & 262 & 393 & - & 0.33 & - & 0.35 & - & 0 & 0.54 & - & 0 & 0.51 & - & 0.30 & - & 0 & 0.29 & - & 0.54 \\
cprover\_software\_analysis/dekker\_vs\_satabs.1 & 41 & 121 & - & 0.21 & - & 0.20 & - & 0 & 0.33 & - & 0 & 0.28 & - & 0.17 & - & 0 & 0.22 & - & 0.28 \\
cprover\_software\_analysis/dekker\_vs\_satabs.2 & 164 & 1345 & - & 0.67 & - & 0.72 & - & 0 & 1.08 & - & 0 & 1.08 & - & 0.62 & - & 0 & 0.61 & - & 1.08 \\
cprover\_software\_analysis/double\_lock\_p1\_vs\_satabs.1 & 64 & 205 & - & 0.22 & - & 0.24 & - & 1 & 0.79 & - & 2 & 1.59 & - & 0.36 & - & 0 & 0.36 & - & 0.79 \\
cprover\_software\_analysis/double\_lock\_p1\_vs\_satabs.2 & 570 & 7601 & - & 4.28 & - & 12.37 & - & 0 & 6.52 & - & 0 & 13.19 & - & 3.29 & - & 0 & 3.19 & - & 6.02 \\
cprover\_software\_analysis/double\_lock\_p1\_vs\_satabs.3 & 570 & 7569 & - & 3.90 & - & 11.20 & - & 0 & 5.76 & - & 0 & 13.13 & - & 3.12 & - & 0 & 3.23 & - & 5.85 \\
cprover\_software\_analysis/double\_lock\_p2\_vs\_satabs.1 & 64 & 213 & - & 0.25 & - & 0.23 & - & 0 & 0.38 & - & 1 & 0.73 & - & 0.20 & - & 0 & 0.22 & - & 0.33 \\
cprover\_software\_analysis/double\_lock\_p2\_vs\_satabs.2 & 184 & 1833 & - & 0.93 & - & 0.93 & - & 0 & 1.44 & - & 0 & 1.44 & - & 0.81 & - & 0 & 0.81 & - & 1.49 \\
cprover\_software\_analysis/double\_lock\_p3\_vs\_satabs.1 & 46 & 81 & - & 0.18 & - & 0.18 & - & 0 & 0.25 & - & 0 & 0.27 & - & 0.15 & - & 0 & 0.16 & - & 0.28 \\
cprover\_software\_analysis/double\_lock\_p3\_vs\_satabs.2 & 112 & 745 & - & 0.49 & - & 0.47 & - & 1 & 1.34 & - & 0 & 0.71 & - & 0.41 & - & 0 & 0.44 & - & 1.33 \\
cprover\_software\_analysis/double\_lock\_p3\_vs\_satabs.3 & 306 & 3137 & - & 1.56 & - & 1.54 & - & 0 & 2.35 & - & 0 & 2.34 & - & 1.32 & - & 0 & 1.32 & - & 2.34 \\
cprover\_software\_analysis/lu-fig2\_fixed\_vs\_satabs.1 & 39 & 37 & - & 0.19 & - & 0.20 & - & 0 & 0.25 & - & 0 & 0.23 & - & 0.17 & - & 0 & 0.13 & - & 0.23 \\
cprover\_software\_analysis/lu-fig2\_fixed\_vs\_satabs.2 & 61 & 185 & - & 0.23 & - & 0.21 & - & 0 & 0.33 & - & 0 & 0.35 & - & 0.20 & - & 0 & 0.23 & - & 0.32 \\
cprover\_software\_analysis/lu-fig2\_fixed\_vs\_satabs.3 & 178 & 1617 & - & 0.82 & - & 0.80 & - & 0 & 1.31 & - & 0 & 1.25 & - & 0.72 & - & 0 & 0.72 & - & 1.25 \\
cprover\_software\_analysis/peterson\_vs\_satabs.1 & 31 & 65 & - & 0.16 & - & 0.17 & - & 0 & 0.25 & - & 0 & 0.25 & - & 0.15 & - & 0 & 0.17 & - & 0.29 \\
cprover\_software\_analysis/peterson\_vs\_satabs.2 & 284 & 1985 & - & 0.95 & - & 0.98 & - & 0 & 1.52 & - & 0 & 1.54 & - & 0.91 & - & 0 & 0.93 & - & 1.54 \\
cprover\_software\_analysis/pthread5\_vs\_satabs.1 & 80 & 413 & - & 0.35 & - & 0.30 & - & 0 & 0.45 & - & 0 & 0.49 & - & 0.27 & - & 0 & 0.28 & - & 0.47 \\
cprover\_software\_analysis/pthread5\_vs\_satabs.2 & 80 & 412 & - & 0.34 & - & 0.35 & - & 0 & 0.47 & - & 0 & 0.47 & - & 0.27 & - & 0 & 0.33 & - & 0.46 \\

>>>>

\usepackage{amsmath}
\usepackage[usenames,dvipsnames]{color}
\usepackage{multirow}
\usepackage{listings}
\usepackage[a4paper, landscape, top=0.5cm, bottom=0.5cm, left=0.5cm, right=0.5cm, includefoot]{geometry}

@@

\begin{description}
  \item[P] Number of places in the petri net.
  \item[T] Number of transitions in the petri net.
  \item[R] Result of our tool. It is + if our tool can prove safety or find an invariant and - otherwise.
  \item[I] Number of iterations. This is the number of traps used for refinement.
  \item[M] Number of minimization steps for the invariant.
  \item[T] Running time of our tool in seconds.
\end{description}

@@

\begin{description}
  \item[Safety] Method Safety over reals.
  \item[Safe-Int] Method Safety over integers.
  \item[Refinement] Method Safety by Refinement over reals.
  \item[Ref-Int] Method Safety by Refinement over integers.
  \item[Invariant] Method Invariant.
  \item[Inv-Min] Method Invariant Minimization.
  \item[Inv-Ref] Method Invariant by Refinement.
  \item[Inv-Ref-Min] Method Invariant by Refinement with Minimization.
\end{description}

@@

The set of benchmarks consists of 77 benchmarks, 26 positive and 51 negative.
Table~\ref{bfc-experiments} and \ref{bfc-experiments-2}
show the experimental results.

@@

  \begin{tabular}{ | l | r | r | *{25}{ r | } } %

@@

         & \multicolumn{2}{|c|}{Safe-Int}

@@

         & \multicolumn{3}{|c|}{Ref-Int}

@@

         & \multicolumn{3}{|c|}{Inv-Ref}
         & \multicolumn{4}{|c|}{Inv-Ref-Min} \\

@@

        & R & M & T

@@

        & R & I & M & T \\

@@

        \multicolumn{25}{|c|}{Positive Benchmarks} \\

@@

cprover-PN/abp & 42 & 43 & + & 0.12 & + & 0.12 & + & 0 & 0.12 & + & 0 & 0.12 & + & 0.22 & + & 2 & 0.44 & + & 0 & 0.32 & + & 0 & 2 & 0.55 \\
cprover-PN/basicME & 18 & 17 & + & 0.11 & + & 0.11 & + & 0 & 0.11 & + & 0 & 0.11 & + & 0.21 & + & 0 & 0.27 & + & 0 & 0.31 & + & 0 & 0 & 0.36 \\
cprover-PN/bingham\_h150 & 309 & 457 & + & 0.31 & + & 0.30 & + & 0 & 0.31 & + & 0 & 0.30 & + & 0.48 & + & 0 & 0.69 & + & 0 & 0.79 & + & 0 & 0 & 0.98 \\
cprover-PN/bingham\_h25 & 59 & 82 & + & 0.13 & + & 0.14 & + & 0 & 0.15 & + & 0 & 0.14 & + & 0.24 & + & 0 & 0.31 & + & 0 & 0.36 & + & 0 & 0 & 0.43 \\
cprover-PN/bingham\_h250 & 509 & 757 & + & 0.47 & + & 0.45 & + & 0 & 0.47 & + & 0 & 0.46 & + & 0.71 & + & 0 & 1.05 & + & 0 & 1.18 & + & 0 & 0 & 1.50 \\
cprover-PN/bingham\_h50 & 109 & 157 & + & 0.17 & + & 0.17 & + & 0 & 0.17 & + & 0 & 0.17 & + & 0.29 & + & 0 & 0.38 & + & 0 & 0.44 & + & 0 & 0 & 0.53 \\
cprover-PN/bingham\_h500 & 1009 & 1507 & + & 0.99 & + & 0.94 & + & 0 & 0.99 & + & 0 & 0.92 & + & 1.45 & + & 0 & 2.35 & + & 0 & 2.44 & + & 0 & 0 & 3.35 \\
cprover-PN/clientserver & 13 & 11 & + & 0.11 & + & 0.11 & + & 0 & 0.11 & + & 0 & 0.11 & + & 0.22 & + & 0 & 0.25 & + & 0 & 0.29 & + & 0 & 0 & 0.35 \\
cprover-PN/csm & 28 & 27 & + & 0.11 & + & 0.11 & + & 0 & 0.12 & + & 0 & 0.12 & + & 0.21 & + & 0 & 0.27 & + & 0 & 0.31 & + & 0 & 0 & 0.37 \\
cprover-PN/gsm & 73 & 156 & + & 0.16 & + & 0.16 & + & 0 & 0.16 & + & 0 & 0.16 & + & 0.27 & + & 0 & 0.35 & + & 0 & 0.41 & + & 0 & 0 & 0.50 \\
cprover-PN/handover & 126 & 255 & + & 0.20 & + & 0.20 & + & 0 & 0.20 & + & 0 & 0.20 & + & 0.31 & + & 0 & 0.43 & + & 0 & 0.50 & + & 0 & 0 & 0.61 \\
cprover-PN/keycard & 59 & 78 & + & 0.13 & + & 0.13 & + & 0 & 0.13 & + & 0 & 0.13 & + & 0.23 & + & 0 & 0.31 & + & 0 & 0.35 & + & 0 & 0 & 0.42 \\
cprover-PN/lamport & 30 & 27 & - & 0.12 & - & 0.12 & - & 0 & 0.18 & - & 0 & 0.18 & - & 0.12 & - & 0 & 0.12 & - & 0 & 0.18 & - & 0 & 0 & 0.18 \\
cprover-PN/mesh2x2 & 66 & 69 & + & 0.13 & + & 0.13 & + & 0 & 0.13 & + & 0 & 0.13 & + & 0.23 & + & 0 & 0.31 & + & 0 & 0.35 & + & 0 & 0 & 0.43 \\
cprover-PN/multipoll & 35 & 41 & + & 0.12 & + & 0.12 & + & 0 & 0.12 & + & 0 & 0.12 & + & 0.23 & + & 0 & 0.28 & + & 0 & 0.33 & + & 0 & 0 & 0.39 \\
cprover-PN/newdekker & 51 & 48 & - & 0.13 & - & 0.13 & - & 0 & 0.19 & - & 0 & 0.19 & - & 0.13 & - & 0 & 0.14 & - & 0 & 0.19 & - & 0 & 0 & 0.19 \\
cprover-PN/newrtp & 12 & 14 & + & 0.11 & + & 0.11 & + & 0 & 0.11 & + & 0 & 0.11 & + & 0.20 & + & 0 & 0.25 & + & 0 & 0.30 & + & 0 & 0 & 0.35 \\
cprover-PN/peterson & 39 & 36 & - & 0.13 & - & 0.13 & - & 0 & 0.19 & - & 0 & 0.19 & - & 0.12 & - & 0 & 0.12 & - & 0 & 0.19 & - & 0 & 0 & 0.18 \\
cprover-PN/phones & 51 & 87 & + & 0.14 & + & 0.13 & + & 0 & 0.13 & + & 0 & 0.14 & + & 0.24 & + & 0 & 0.31 & + & 0 & 0.36 & + & 0 & 0 & 0.43 \\
cprover-PN/reaction & 19 & 15 & + & 0.11 & + & 0.11 & + & 0 & 0.11 & + & 0 & 0.11 & + & 0.20 & + & 0 & 0.26 & + & 0 & 0.30 & + & 0 & 0 & 0.35 \\
cprover-PN/reaction3 & 22 & 18 & + & 0.12 & + & 0.11 & + & 0 & 0.11 & + & 0 & 0.11 & + & 0.20 & + & 0 & 0.26 & + & 0 & 0.30 & + & 0 & 0 & 0.36 \\
cprover-PN/reaction4 & 16 & 13 & + & 0.11 & + & 0.11 & + & 0 & 0.12 & + & 0 & 0.11 & + & 0.20 & + & 0 & 0.26 & + & 0 & 0.29 & + & 0 & 0 & 0.35 \\
cprover-PN/read-write & 36 & 31 & + & 0.12 & + & 0.12 & + & 0 & 0.12 & + & 0 & 0.12 & + & 0.21 & + & 0 & 0.29 & + & 0 & 0.32 & + & 0 & 0 & 0.38 \\
cprover-PN/restriction & 15 & 10 & + & 0.11 & + & 0.11 & + & 0 & 0.11 & + & 0 & 0.11 & + & 0.20 & + & 0 & 0.26 & + & 0 & 0.29 & + & 0 & 0 & 0.35 \\
cprover\_sa/conditionals\_vs\_satabs.2 & 214 & 281 & + & 0.21 & + & 0.22 & + & 0 & 0.21 & + & 0 & 0.21 & + & 0.34 & + & 0 & 0.47 & + & 0 & 0.54 & + & 0 & 0 & 0.68 \\
cprover\_sa/rand\_cas\_vs\_satabs.2 & 110 & 139 & + & 0.16 & + & 0.15 & + & 0 & 0.16 & + & 0 & 0.16 & + & 0.26 & + & 0 & 0.36 & + & 0 & 0.42 & + & 0 & 0 & 0.50 \\

@@

        \multicolumn{25}{|c|}{Negative Benchmarks} \\

@@

cprover-PN/kanban & 26 & 29 & - & 0.12 & - & 0.12 & - & 0 & 0.18 & - & 0 & 0.18 & - & 0.12 & - & 0 & 0.12 & - & 0 & 0.18 & - & 0 & 0 & 0.18 \\
cprover-PN/leabasicapproach & 30 & 27 & - & 0.12 & - & 0.12 & - & 0 & 0.18 & - & 0 & 0.18 & - & 0.12 & - & 0 & 0.12 & - & 0 & 0.18 & - & 0 & 0 & 0.18 \\
cprover-PN/platoon & 20 & 17 & - & 0.12 & - & 0.12 & - & 0 & 0.17 & - & 0 & 0.17 & - & 0.11 & - & 0 & 0.11 & - & 0 & 0.17 & - & 0 & 0 & 0.17 \\
cprover-PN/platoonFiniteHandlerPoly & 19 & 16 & - & 0.12 & - & 0.12 & - & 0 & 0.18 & - & 0 & 0.17 & - & 0.11 & - & 0 & 0.11 & - & 0 & 0.17 & - & 0 & 0 & 0.17 \\
cprover-PN/pncsacover & 64 & 68 & - & 0.14 & - & 0.14 & - & 0 & 0.21 & - & 0 & 0.21 & - & 0.14 & - & 0 & 0.14 & - & 0 & 0.21 & - & 0 & 0 & 0.22 \\
cprover-PN/reaction2 & 13 & 11 & - & 0.12 & - & 0.12 & - & 0 & 0.17 & - & 0 & 0.17 & - & 0.11 & - & 0 & 0.11 & - & 0 & 0.16 & - & 0 & 0 & 0.17 \\
cprover-PN/reaction5 & 11 & 8 & - & 0.11 & - & 0.12 & - & 1 & 0.32 & - & 1 & 0.32 & - & 0.11 & - & 0 & 0.11 & - & 1 & 0.32 & - & 1 & 0 & 0.32 \\
cprover\_sa/Boop\_simple\_vf\_satabs.1 & 31 & 31 & - & 0.12 & - & 0.12 & - & 0 & 0.18 & - & 0 & 0.18 & - & 0.12 & - & 0 & 0.12 & - & 0 & 0.18 & - & 0 & 0 & 0.18 \\
cprover\_sa/Boop\_simple\_vf\_satabs.2 & 330 & 7489 & - & 2.67 & - & 2.68 & - & 0 & 4.28 & - & 0 & 4.29 & - & 2.44 & - & 0 & 2.43 & - & 0 & 4.30 & - & 0 & 0 & 4.29 \\
cprover\_sa/Function\_Pointer3\_vs\_satabs.1 & 40 & 71 & - & 0.14 & - & 0.14 & - & 1 & 0.40 & - & 1 & 0.40 & - & 0.13 & - & 0 & 0.13 & - & 1 & 0.40 & - & 1 & 0 & 0.40 \\
cprover\_sa/Function\_Pointer3\_vs\_satabs.2 & 306 & 841 & - & 0.43 & - & 0.44 & - & 0 & 0.65 & - & 1 & 1.26 & - & 0.39 & - & 0 & 0.39 & - & 0 & 0.67 & - & 0 & 0 & 0.67 \\
cprover\_sa/Function\_Pointer3\_vs\_satabs.3 & 2826 & 8961 & - & 6.26 & - & 7.02 & - & 0 & 8.30 & - & 0 & 8.89 & - & 5.90 & - & 0 & 5.82 & - & 0 & 8.14 & - & 0 & 0 & 8.19 \\

@@

        \multicolumn{25}{|c|}{Negative Benchmarks (continued)} \\

@@

cprover\_sa/buggy\_spaghetti\_vf\_satabs.1 & 78 & 115 & - & 0.16 & - & 0.16 & - & 0 & 0.23 & - & 0 & 0.23 & - & 0.14 & - & 0 & 0.14 & - & 0 & 0.23 & - & 0 & 0 & 0.23 \\
cprover\_sa/buggy\_spaghetti\_vf\_satabs.2 & 326 & 697 & - & 0.41 & - & 0.40 & - & 0 & 0.61 & - & 0 & 0.61 & - & 0.36 & - & 0 & 0.36 & - & 0 & 0.60 & - & 0 & 0 & 0.60 \\
cprover\_sa/conditionals\_vs\_satabs.1 & 50 & 55 & - & 0.14 & - & 0.14 & - & 0 & 0.20 & - & 0 & 0.20 & - & 0.13 & - & 0 & 0.12 & - & 0 & 0.19 & - & 0 & 0 & 0.19 \\
cprover\_sa/constants\_vf\_satabs.1 & 26 & 25 & - & 0.12 & - & 0.12 & - & 0 & 0.17 & - & 0 & 0.17 & - & 0.11 & - & 0 & 0.12 & - & 0 & 0.17 & - & 0 & 0 & 0.17 \\
cprover\_sa/constants\_vf\_satabs.2 & 262 & 393 & - & 0.27 & - & 0.27 & - & 0 & 0.41 & - & 0 & 0.42 & - & 0.25 & - & 0 & 0.24 & - & 0 & 0.41 & - & 0 & 0 & 0.42 \\
cprover\_sa/dekker\_vs\_satabs.1 & 41 & 121 & - & 0.15 & - & 0.16 & - & 0 & 0.23 & - & 0 & 0.24 & - & 0.14 & - & 0 & 0.14 & - & 0 & 0.23 & - & 0 & 0 & 0.23 \\
cprover\_sa/dekker\_vs\_satabs.2 & 164 & 1345 & - & 0.56 & - & 0.57 & - & 0 & 0.88 & - & 0 & 0.88 & - & 0.50 & - & 0 & 0.50 & - & 0 & 0.88 & - & 0 & 0 & 0.89 \\
cprover\_sa/double\_lock\_p1\_vs\_satabs.1 & 64 & 205 & - & 0.19 & - & 0.19 & - & 1 & 0.54 & - & 2 & 0.81 & - & 0.17 & - & 0 & 0.17 & - & 1 & 0.54 & - & 1 & 0 & 0.54 \\
cprover\_sa/double\_lock\_p1\_vs\_satabs.2 & 570 & 7601 & - & 3.29 & - & 10.49 & - & 0 & 4.91 & - & 0 & 12.05 & - & 2.59 & - & 0 & 2.65 & - & 0 & 4.89 & - & 0 & 0 & 4.87 \\
cprover\_sa/double\_lock\_p1\_vs\_satabs.3 & 570 & 7569 & - & 3.15 & - & 10.34 & - & 0 & 4.70 & - & 0 & 11.86 & - & 2.59 & - & 0 & 2.60 & - & 0 & 4.69 & - & 0 & 0 & 4.68 \\
cprover\_sa/double\_lock\_p2\_vs\_satabs.1 & 64 & 213 & - & 0.19 & - & 0.20 & - & 0 & 0.28 & - & 1 & 0.57 & - & 0.18 & - & 0 & 0.17 & - & 0 & 0.28 & - & 0 & 0 & 0.28 \\
cprover\_sa/double\_lock\_p2\_vs\_satabs.2 & 184 & 1833 & - & 0.78 & - & 0.77 & - & 0 & 1.18 & - & 0 & 1.17 & - & 0.67 & - & 0 & 0.66 & - & 0 & 1.18 & - & 0 & 0 & 1.18 \\
cprover\_sa/double\_lock\_p3\_vs\_satabs.1 & 46 & 81 & - & 0.14 & - & 0.14 & - & 0 & 0.21 & - & 0 & 0.21 & - & 0.13 & - & 0 & 0.13 & - & 0 & 0.21 & - & 0 & 0 & 0.21 \\
cprover\_sa/double\_lock\_p3\_vs\_satabs.2 & 112 & 745 & - & 0.37 & - & 0.38 & - & 1 & 1.06 & - & 0 & 0.58 & - & 0.33 & - & 0 & 0.34 & - & 1 & 1.07 & - & 1 & 0 & 1.07 \\
cprover\_sa/double\_lock\_p3\_vs\_satabs.3 & 306 & 3137 & - & 1.28 & - & 1.28 & - & 0 & 1.93 & - & 0 & 1.92 & - & 1.08 & - & 0 & 1.09 & - & 0 & 1.92 & - & 0 & 0 & 1.94 \\
cprover\_sa/lu-fig2\_vs\_satabs.1 & 39 & 37 & - & 0.14 & - & 0.13 & - & 0 & 0.19 & - & 0 & 0.18 & - & 0.12 & - & 0 & 0.12 & - & 0 & 0.19 & - & 0 & 0 & 0.19 \\
cprover\_sa/lu-fig2\_vs\_satabs.2 & 61 & 185 & - & 0.18 & - & 0.18 & - & 0 & 0.27 & - & 0 & 0.27 & - & 0.17 & - & 0 & 0.17 & - & 0 & 0.27 & - & 0 & 0 & 0.27 \\
cprover\_sa/lu-fig2\_vs\_satabs.3 & 178 & 1617 & - & 0.69 & - & 0.71 & - & 0 & 1.03 & - & 0 & 1.04 & - & 0.59 & - & 0 & 0.60 & - & 0 & 1.03 & - & 0 & 0 & 1.03 \\
cprover\_sa/peterson\_vs\_satabs.1 & 31 & 65 & - & 0.14 & - & 0.14 & - & 0 & 0.20 & - & 0 & 0.20 & - & 0.13 & - & 0 & 0.13 & - & 0 & 0.21 & - & 0 & 0 & 0.20 \\
cprover\_sa/peterson\_vs\_satabs.2 & 284 & 1985 & - & 0.81 & - & 0.83 & - & 0 & 1.24 & - & 0 & 1.27 & - & 0.73 & - & 0 & 0.81 & - & 0 & 1.26 & - & 0 & 0 & 1.24 \\
cprover\_sa/pthread5\_vs\_satabs.1 & 80 & 413 & - & 0.26 & - & 0.26 & - & 0 & 0.38 & - & 0 & 0.41 & - & 0.24 & - & 0 & 0.23 & - & 0 & 0.39 & - & 0 & 0 & 0.39 \\
cprover\_sa/pthread5\_vs\_satabs.2 & 80 & 412 & - & 0.25 & - & 0.26 & - & 0 & 0.39 & - & 0 & 0.39 & - & 0.24 & - & 0 & 0.23 & - & 0 & 0.38 & - & 0 & 0 & 0.39 \\
cprover\_sa/pthread5\_vs\_satabs.3 & 187 & 1893 & - & 0.79 & - & 0.79 & - & 0 & 1.21 & - & 0 & 1.20 & - & 0.68 & - & 0 & 0.67 & - & 0 & 1.21 & - & 0 & 0 & 1.22 \\
cprover\_sa/pthread5\_vs\_satabs.4 & 187 & 1889 & - & 0.78 & - & 0.78 & - & 0 & 1.20 & - & 0 & 1.21 & - & 0.67 & - & 0 & 0.67 & - & 0 & 1.19 & - & 0 & 0 & 1.22 \\
